---
title: "DC.1 DURIN TOMST Logger Data Cleaning"
author: "OUDINA Yanis"
date: "05/06/2023"
output: html_notebook
---

To start, you should simply install all the packages requiered to run the code.
```{r install_packages}
install.packages("tidyverse")
install.packages("lubridate")
install.packages("dataDownloader")
install.packages("purrrlyr")
install.packages("readxl")
install.packages("fs")
install.packages("purrr")
install.packages("readr")
install.packages("ggplot2")
```

And to load them.

```{r load_packages}

source("https://raw.githubusercontent.com/audhalbritter/Three-D/master/R/Climate/soilmoisture_correction.R")
library(tidyverse)
library(lubridate)
# library(dataDownloader)
library(purrrlyr)
library(readxl)
library(fs)
library(purrr)
library(readr)
library(ggplot2)
source("soilmoisture_correction.R")
```

This section is the one importing the data: metadata & loggers data.
You may have to change this depending on where your data are. You can also import them directly from OSF if the "Datadownloader" package is working.

It also makes small changes on the data naming/format.

```{r import_data}

# Read in meta data
metatomst <- read_excel(path="durin_tomst_microclimate_loggers_metadata.xlsx", col_names=TRUE, col_types=c("text","text","numeric","text","text","numeric","text","text","numeric","numeric","date","date","numeric","text","numeric","text","numeric","text","numeric","text","text"))#

# Change formats
# Date format to day/month/year in 01/12/1990 format
# PlotID and LoggerID to factor to match later scripts$
metatomst$date_in <- format(metatomst$date_in, "%d/%m/%Y")
metatomst$date_out <- format(metatomst$date_out, "%d/%m/%Y")
metatomst$loggerID <- as.factor(metatomst$loggerID)
metatomst$plotID <- as.factor(as.numeric(metatomst$plotID))
# Check loggerID and plotID's as they don't seem to stay correct format.
#unique(metatomst$loggerID) # Should be 116
#unique(metatomst$plotID) # Should be 1.1, 1.2, 1.3 >> 9.1, 9.2, 9.3 for 27 unique values

### Read in files
files <- dir(path = "data/loggers_data/not_drought", pattern = "^data.*\\.csv$", full.names = TRUE, recursive = TRUE)

temp_raw <- map_df(set_names(files), function(file) {
  file %>%
    set_names() %>%
    map_dfr(~ read_csv2(file = file,
                        col_names = FALSE,
                        # specify column types as not all .csv's match
                        # some examples of doubles and integers in X4
                        col_types = "n?nnnnnn"))
}, .id = "file")

files2 <- dir(path = "data/loggers_data/lygra2", pattern = "^data.*\\.csv$", full.names = TRUE, recursive = TRUE)

temp_raw2 <- map_df(set_names(files2), function(file) {
  file %>%
    set_names() %>%
    map_dfr(~ read_csv2(file = file,
                        col_names = FALSE,
                        # specify column types as not all .csv's match
                        # some examples of doubles and integers in X4
                        col_types = "n?nnnnnn"))
}, .id = "file")




```

Here the data are read in the TOMST loggers files and create new objects to work on.

```{r read_organize_data}
microclimate <- temp_raw %>%
  # rename column names
  rename("ID" = "file", "datetime" = "X2", "time_zone" = "X3", "soil_temperature" = "X4", "ground_temperature" = "X5", "air_temperature" = "X6", "RawSoilmoisture" = "X7", "Shake" = "X8", "ErrorFlag" = "X9") %>%
  # change the date and time format
  mutate(datetime = ymd_hm(datetime)) %>%

  # get logger ID by trimming characters from the file name
  mutate(
    loggerID = substr(ID, nchar(ID)-24, nchar(ID)-17),
    loggerID = as.factor(loggerID)
  ) %>%
  select(!c(ID, X1,X10)) %>% # remove unnessary columns
  distinct() %>%  # only choose unique records
  left_join(metatomst, by = "loggerID",relationship="many-to-many") %>%
   group_by(loggerID) %>%
  filter(
     datetime > "2023-04-23 00:00:01"
   ) %>%

 #soil moisture calibration
  mutate( # calculate soil moisture
    soil_moisture = soil.moist(
      rawsoilmoist = RawSoilmoisture,
      soil_temp = soil_temperature,
      soilclass = "silt_loam" #it is the closest soil class, but still very wrong. The TMS calibration tool does not have any class for our soil
    )) %>%
  select(!c(RawSoilmoisture)) %>% # we want vertical tidy data

    # Choose and order columns to keep for a wide-format database
    select(c(datetime, site, fire_class, drt_treatment, site_type,land_type, plotID, gps_loc, species, plantID,
             loggerID, date_in, date_out, h_t_left,c_t_l,h_t_r,c_t_l,h_b_l,c_b_l,h_b_r,c_b_r,
             air_temperature, ground_temperature, soil_temperature, soil_moisture,
             Shake, ErrorFlag))
  # Save clean file
   current_time <- format(Sys.time(), "%d%m%Y_%H%M%S")
   write_csv(microclimate, file = paste("data/DURIN_clean_microclimate_2023_",current_time,".csv"))
  
microclimate <- microclimate %>%
  select(c(datetime, site, fire_class, drt_treatment, site_type,land_type, plotID, gps_loc, species, plantID,
             loggerID, date_in, date_out, h_t_left,c_t_l,h_t_r,c_t_l,h_b_l,c_b_l,h_b_r,c_b_r,
             air_temperature, ground_temperature, soil_temperature, soil_moisture,
             Shake, ErrorFlag)) %>%

  pivot_longer(cols = c(air_temperature, soil_temperature, ground_temperature, soil_moisture), names_to = "sensor", values_to = "value")


microclimate2 <- temp_raw2 %>%
  # rename column names
  rename("ID" = "file", "datetime" = "X2", "time_zone" = "X3", "soil_temperature" = "X4", "ground_temperature" = "X5", "air_temperature" = "X6", "RawSoilmoisture" = "X7", "Shake" = "X8", "ErrorFlag" = "X9") %>%
  # change the date and time format
  mutate(datetime = ymd_hm(datetime)) %>%

  # get logger ID by trimming characters from the file name
  mutate(
    loggerID = substr(ID, nchar(ID)-24, nchar(ID)-17),
    loggerID = as.factor(loggerID)
  ) %>%
  select(!c(ID, X1,X10)) %>% # remove unnessary columns
  distinct() %>%  # only choose unique records
  left_join(metatomst, by = "loggerID",relationship="many-to-many") %>%
   group_by(loggerID) %>%
  filter(
     datetime > "2023-04-23 00:00:01"
   ) %>%

 #soil moisture calibration
  mutate( # calculate soil moisture
    soil_moisture = soil.moist(
      rawsoilmoist = RawSoilmoisture,
      soil_temp = soil_temperature,
      soilclass = "silt_loam" #it is the closest soil class, but still very wrong. The TMS calibration tool does not have any class for our soil
    )) %>%
  select(!c(RawSoilmoisture)) %>% # we want vertical tidy data

    # Choose and order columns to keep for a wide-format database
    select(c(datetime, site, fire_class, drt_treatment, site_type,land_type, plotID, gps_loc, species, plantID,
             loggerID, date_in, date_out, h_t_left,c_t_l,h_t_r,c_t_l,h_b_l,c_b_l,h_b_r,c_b_r,
             air_temperature, ground_temperature, soil_temperature, soil_moisture,
             Shake, ErrorFlag))
  # Save clean file
   current_time <- format(Sys.time(), "%d%m%Y_%H%M%S")
   write_csv(microclimate, file = paste("data/DURIN_clean_microclimate_2023_",current_time,".csv"))
  
microclimate2 <- microclimate2 %>%
  select(c(datetime, site, fire_class, drt_treatment, site_type,land_type, plotID, gps_loc, species, plantID,
             loggerID, date_in, date_out, h_t_left,c_t_l,h_t_r,c_t_l,h_b_l,c_b_l,h_b_r,c_b_r,
             air_temperature, ground_temperature, soil_temperature, soil_moisture,
             Shake, ErrorFlag)) %>%

  pivot_longer(cols = c(air_temperature, soil_temperature, ground_temperature, soil_moisture), names_to = "sensor", values_to = "value")


microclimate <- microclimate %>%
  mutate(date_in = as.Date(date_in, format="%d/%m/%Y")) 

microclimate2 <- microclimate2 %>%
    mutate(date_in = as.Date(date_in, format="%d/%m/%Y"))

gc()


```

The objective of this section is to clean the data as much as possible before. In order to do this, we will try to avoid errors of measurements. They can be multiple (e.g bad calibration, aberrant measure,...)

Each measure will then have a specific "cutting" code: keep, cut, suspicious that is linked to the way we will treat these data.

Also, here is a list of loggers having shown some problems:
94195238 - soil_moisture
94195237 - air_temperature
95221050 - soil_temperature
94195238 - soil_moisture

```{r data_cleaning}
microclimate <- microclimate %>% 
  mutate(
    cutting = case_when(
      # air temperature cleaning
      sensor == "air_temperature" & value < -20 ~ "cut",

      # soil temperature cleaning
      sensor == "soil_temperature" & value < -20 ~ "cut",

      # ground temperature cleaning
      sensor == "ground_temperature" & value < -20 ~ "cut",

      # soil moisture cleaning
      sensor == "soil_moisture" & value <= 0 ~ "cut",
      
      # soil moisture cleaning
      sensor == "soil_moisture" & value >= 1 ~ "cut",

      TRUE ~ "keep"
    )
  )

microclimate2 <- microclimate2 %>% 
  mutate(
    cutting = case_when(
      # air temperature cleaning
      sensor == "air_temperature" & value < -20 ~ "cut",

      # soil temperature cleaning
      sensor == "soil_temperature" & value < -20 ~ "cut",

      # ground temperature cleaning
      sensor == "ground_temperature" & value < -20 ~ "cut",

      # soil moisture cleaning
      sensor == "soil_moisture" & value <= 0 ~ "cut",
      
      # soil moisture cleaning
      sensor == "soil_moisture" & value >= 1 ~ "cut",

      TRUE ~ "keep"
    )
  )
```

Here, this will save you data for logger and stock them as .png plots. You will have one file per plotID (1.1, 1.2, ... ) per data (soil_moisture, soil_temp....) and 

```{r plot_data_plotID_sensor_species}
# #soil temperature
for (i in 1:9) {
  for (j in 1:3) {
    plot_number <- i + j/10
    file_name <- paste("loggers_soil_temperature_", as.character(i), "_", as.character(j), ".png", sep = "")

    filtered_data <- microclimate %>%
      filter(
        sensor == "soil_temperature" &
          datetime > "2023-04-22" &
          plotID == plot_number &
          cutting != "cut"
      ) %>%
      group_by(loggerID) %>%
      mutate(logger_species = paste(loggerID, site, plotID, drt_treatment, species, sep = " ")) # Add the column "logger_species" containing the concatenation of "loggerID", "plotID", "drt_treatment", and "species"

    plot <- ggplot(filtered_data, aes(x = datetime, y = value, color = "cutting")) +
      geom_line(aes(group = logger_species)) +
      scale_color_manual(values = c(
        "keep" = "#1e90ff",
        "suspect" = "#ff0800"
      )) +
      scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
      facet_wrap(vars(logger_species), ncol = 3, scales = "free") # Use the column "logger_species" for facet_wrap

    ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")
  }
}

#ground_temperature
for (i in 1:9) {
  for (j in 1:3) {
    plot_number <- i + j/10
    file_name <- paste("loggers_ground_temperature_", as.character(i), "_", as.character(j), ".png", sep = "")

    filtered_data <- microclimate %>%
      filter(
        sensor == "ground_temperature" &
          datetime > "2023-04-22" &
          plotID == plot_number &
          cutting != "cut"
      ) %>%
      group_by(loggerID) %>%
      mutate(logger_species = paste(loggerID, site, plotID, drt_treatment, species, sep = " ")) # Add the column "logger_species" containing the concatenation of "loggerID", "plotID", "drt_treatment", and "species"

    plot <- ggplot(filtered_data, aes(x = datetime, y = value, color = "cutting")) +
      geom_line(aes(group = logger_species)) +
      scale_color_manual(values = c(
        "keep" = "#1e90ff",
        "suspect" = "#ff0800"
      )) +
      scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
      facet_wrap(vars(logger_species), ncol = 3, scales = "free") # Use the column "logger_species" for facet_wrap

    ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")
  }
}

#air_temperature
for (i in 1:9) {
  for (j in 1:3) {
    plot_number <- i + j/10
    file_name <- paste("loggers_air_temperature_", as.character(i), "_", as.character(j), ".png", sep = "")

    filtered_data <- microclimate %>%
      filter(
        sensor == "air_temperature" &
          datetime > "2023-04-22" &
          plotID == plot_number &
          cutting != "cut"
      ) %>%
      group_by(loggerID) %>%
      mutate(logger_species = paste(loggerID, site, plotID, drt_treatment, species, sep = " ")) # Add the column "logger_species" containing the concatenation of "loggerID", "plotID", "drt_treatment", and "species"

    plot <- ggplot(filtered_data, aes(x = datetime, y = value, color = "cutting")) +
      geom_line(aes(group = logger_species)) +
      scale_color_manual(values = c(
        "keep" = "#1e90ff",
        "suspect" = "#ff0800"
      )) +
      scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
      facet_wrap(vars(logger_species), ncol = 3, scales = "free") # Use the column "logger_species" for facet_wrap

    ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")
  }
}



#soil_moisture
for (i in 1:9) {
  for (j in 1:3) {
    plot_number <- i + j/10
    file_name <- paste("loggers_soil_moisture_", as.character(i), "_", as.character(j), ".png", sep = "")

    filtered_data <- microclimate %>%
      filter(
        sensor == "soil_moisture" &
          datetime > "2023-04-22" &
          plotID == plot_number &
          cutting != "cut"
      ) %>%
      group_by(loggerID) %>%
      mutate(logger_species = paste(loggerID, site, plotID, drt_treatment, species, sep = " ")) # Add the column "logger_species" containing the concatenation of "loggerID", "plotID", "drt_treatment", and "species"

    plot <- ggplot(filtered_data, aes(x = datetime, y = value, color = "cutting")) +
      geom_line(aes(group = logger_species)) +
      scale_color_manual(values = c(
        "keep" = "#1e90ff",
        "suspect" = "#ff0800"
      )) +
      scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
      facet_wrap(vars(logger_species), ncol = 3, scales = "free") # Use the column "logger_species" for facet_wrap

    ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")
  }
}
```

Same, here the goal is to plot the data. The goal is to sort the .png by plotID, to have only 1 plot per png but to have the 3 to 5 species on it.

```{r plot_data_plotID_sensor_merged}
# #soil temperature
for (i in 1:9) {
  for (j in 1:3) {
    plot_number <- i + j/10
    file_name <- paste("loggers_soil_temperature_test", as.character(i), "_", as.character(j), ".png", sep = "")

    filtered_data <- microclimate %>%
      filter(
        sensor == "soil_temperature" &
          datetime > "2023-04-23" &
          plotID == plot_number 
          #cutting != "cut"
      ) %>%
      group_by(loggerID) %>%
      mutate(logger_species = paste(loggerID, site, plotID, drt_treatment, sep = " "))

    plot <- ggplot(filtered_data, aes(x = datetime, y = value)) +
      geom_line(aes(group = loggerID, color = species)) +
      scale_color_manual(values = c(
          "Control" = "#7876B1",
      "Calluna vulgaris" = "#E18727",
      "Empetrum nigrum" = "#20854E",
      "Vaccinium vitis idea" = "#BC3C29",
      "Vaccinium myrtillus" = "#0072B5"
      )) +
      scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
     # Specify the x, y and colour axis labels, rather than using default names from dataset
      labs(x = "Date", y = " Air Temperature (Celsius)", colour = "Focal Species")
      ylim(-2,40)

      ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")
  }
}

#ground_temperature
for (i in 1:9) {
  for (j in 1:3) {
    plot_number <- i + j/10
    file_name <- paste("loggers_ground_temperature_test", as.character(i), "_", as.character(j), ".png", sep = "")

    filtered_data <- microclimate %>%
      filter(
        sensor == "ground_temperature" &
          datetime > "2023-04-23" &
          plotID == plot_number 
         # cutting != "cut"
      ) %>%
      group_by(loggerID) %>%
      mutate(logger_species = paste(loggerID, site, plotID, drt_treatment, sep = " "))

    plot <- ggplot(filtered_data, aes(x = datetime, y = value)) +
      geom_line(aes(group = loggerID, color = species)) +
      scale_color_manual(values = c(
         "Control" = "#7876B1",
      "Calluna vulgaris" = "#E18727",
      "Empetrum nigrum" = "#20854E",
      "Vaccinium vitis idea" = "#BC3C29",
      "Vaccinium myrtillus" = "#0072B5"
      )) +
      scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
     # Specify the x, y and colour axis labels, rather than using default names from dataset
      labs(x = "Date", y = " Air Temperature (Celsius)", colour = "Focal Species")
      ylim(-2,40)

      ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")
  }
}


#air_temperature
for (i in 1:9) {
  for (j in 1:3) {
    plot_number <- i + j/10
    file_name <- paste("loggers_air_temperature_test", as.character(i), "_", as.character(j), ".png", sep = "")

    filtered_data <- microclimate %>%
      filter(
        sensor == "air_temperature" &
          datetime > "2023-04-23" &
          plotID == plot_number 
         # cutting != "cut"
      ) %>%
      group_by(loggerID) %>%
      mutate(logger_species = paste(loggerID, site, plotID, drt_treatment, sep = " "))

    plot <- ggplot(filtered_data, aes(x = datetime, y = value)) +
      geom_line(aes(group = loggerID, color = species)) +
      scale_color_manual(values = c(
          "Control" = "#7876B1",
      "Calluna vulgaris" = "#E18727",
      "Empetrum nigrum" = "#20854E",
      "Vaccinium vitis idea" = "#BC3C29",
      "Vaccinium myrtillus" = "#0072B5"
      )) +
      scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
     # Specify the x, y and colour axis labels, rather than using default names from dataset
      labs(x = "Date", y = " Ground Temperature (Celsius)", colour = "Focal Species")
      ylim(-2,40)

      ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")
  }
}


#soil_moisture
for (i in 1:9) {
  for (j in 1:3) {
    plot_number <- i + j/10
    file_name <- paste("loggers_soil_moisture_test", as.character(i), "_", as.character(j), ".png", sep = "")

    filtered_data <- microclimate %>%
      filter(
        sensor == "soil_moisture" &
          datetime > "2023-04-23" &
          plotID == plot_number 
         # cutting != "cut"
      ) %>%
      group_by(loggerID) %>%
      mutate(logger_species = paste(loggerID, site, plotID, drt_treatment, sep = " "))

    plot <- ggplot(filtered_data, aes(x = datetime, y = value)) +
      geom_line(aes(group = loggerID, color = species)) +
      scale_color_manual(values = c(
        "Control" = "#7876B1",
        "Calluna vulgaris" = "#E18727",
        "Empetrum nigrum" = "#20854E",
        "Vaccinium vitis idea" = "#BC3C29",
        "Vaccinium myrtillus" = "#0072B5"
      )) +
      scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
     # Specify the x, y and colour axis labels, rather than using default names from dataset
      labs(x = "Date", y = " Soil Moisture ()", colour = "Focal Species")
      ylim(0.15,0.6)

      ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")
  }
}
```

here the goal is at the end to have 3 .png with 9 plots, each plot has 5 species and it and they are ordered by drt_treatment and by the replicate number.

```{r plot_data_drought_aged_specie}
#air temperature
age_vector <- c("Pioneer", "Building", "Mature")
for (i in 1:3) {
  file_name <- paste("loggers_air_temperature_", age_vector[i], ".png", sep = "")
  
  filtered_data <- microclimate %>%
    filter(
      sensor == "air_temperature" &
        datetime > "2023-04-23" &
        fire_class == age_vector[i] &
        cutting != "cut" 
    ) %>%
    group_by(fire_class)  

  plot <- ggplot(filtered_data, aes(x = datetime, y = value)) +
    geom_line(aes(group = loggerID, color = species)) +
    scale_color_manual(values = c(
      "Control" = "#7876B1",
      "Calluna vulgaris" = "#E18727",
      "Empetrum nigrum" = "#20854E",
      "Vaccinium vitis idea" = "#BC3C29",
      "Vaccinium myrtillus" = "#0072B5"
    )) +
    scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
    facet_grid(drt_treatment ~ substring(as.character(plotID), first = 1, last = 1), scale="free") +
    labs(x = "Date", y = " Air Temperature (Celsius)")+
    ylim(-10, 30)
  
  ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")
}

#ground temperature
age_vector <- c("Pioneer", "Building", "Mature")
for (i in 1:3) {
  file_name <- paste("loggers_ground_temperature_", age_vector[i], ".png", sep = "")
  
  filtered_data <- microclimate %>%
    filter(
      sensor == "ground_temperature" &
        datetime > "2023-04-23" &
        fire_class == age_vector[i] &
        cutting != "cut" 
    ) %>%
    group_by(fire_class)  

  plot <- ggplot(filtered_data, aes(x = datetime, y = value)) +
    geom_line(aes(group = loggerID, color = species)) +
    scale_color_manual(values = c(
      "Control" = "#7876B1",
      "Calluna vulgaris" = "#E18727",
      "Empetrum nigrum" = "#20854E",
      "Vaccinium vitis idea" = "#BC3C29",
      "Vaccinium myrtillus" = "#0072B5"
    )) +
    scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
    facet_grid(drt_treatment ~ substring(as.character(plotID), first = 1, last = 1), scale="free") +
    labs(x = "Date", y = " Ground Temperature (Celsius)")+
    ylim(-10, 30)
  
  ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")
}

#soil temp
age_vector <- c("Pioneer", "Building", "Mature")
for (i in 1:3) {
  file_name <- paste("loggers_soil_temperature_", age_vector[i], ".png", sep = "")
  
  filtered_data <- microclimate %>%
    filter(
      sensor == "soil_temperature" &
        datetime > "2023-04-23" &
        fire_class == age_vector[i] &
        cutting != "cut" 
    ) %>%
    group_by(fire_class)  

  plot <- ggplot(filtered_data, aes(x = datetime, y = value)) +
    geom_line(aes(group = loggerID, color = species)) +
    scale_color_manual(values = c(
      "Control" = "#7876B1",
      "Calluna vulgaris" = "#E18727",
      "Empetrum Nigrum" = "#20854E",
      "Vaccinium vitis idea" = "#BC3C29",
      "Vaccinium myrtillus" = "#0072B5"
    )) +
    scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
    facet_grid(drt_treatment ~ substring(as.character(plotID), first = 1, last = 1), scale="free") +
    labs(x = "Date", y = " Soil Temperature (Celsius)")+
    ylim(-10, 30)
  
  ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")
}

#soil moisture
age_vector <- c("Pioneer", "Building", "Mature")
for (i in 1:3) {
  file_name <- paste("loggers_soil_moisture_", age_vector[i], ".png", sep = "")
  
  filtered_data <- microclimate %>%
    filter(
      sensor == "soil_moisture" &
        datetime > "2023-04-23" &
        fire_class == age_vector[i] &
        cutting != "cut" 
    ) %>%
    group_by(fire_class)  

  plot <- ggplot(filtered_data, aes(x = datetime, y = value)) +
    geom_line(aes(group = loggerID, color = species)) +
    scale_color_manual(values = c(
      "Control" = "#7876B1",
      "Calluna vulgaris" = "#E18727",
      "Empetrum nigrum" = "#20854E",
      "Vaccinium vitis idea" = "#BC3C29",
      "Vaccinium myrtillus" = "#0072B5"
    )) +
    scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
    facet_grid(drt_treatment ~ substring(as.character(plotID), first = 1, last = 1), scale="free") +
    ylim(0.10, 0.6)
  
  ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")
}
```

Here the goal is to compare the differences between the 3 fire_classes. The first code makes 3 separate plots, the second one plots everything on the same


```{r control_fire_class_comparaison}
#air_temp
file_name <- paste("loggers_air_temperature_control_comparaison", age_vector[i], ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "air_temperature" &
      datetime > "2023-04-23" &
      species == "Control" &
      cutting != "cut" 
  ) %>%
  group_by(datetime, fire_class, species) %>%
  summarize(mean_value = mean(value))


plot <- ggplot(filtered_data, aes(x = datetime, y = mean_value)) +
  geom_line(aes(group = fire_class, color = species)) +
  scale_color_manual(values = c(
    "Control" = "#7876B1"
  )) +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
  facet_wrap(vars(fire_class), ncol = 3, scales = "free") +
  labs(x = "Date", y = " Air Temperature (Celsius)")+
  ylim(-10, 30)

ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")


##ground temp
file_name <- paste("loggers_ground_temperature_control_comparaison", age_vector[i], ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "ground_temperature" &
      datetime > "2023-04-23" &
      species == "Control" &
      cutting != "cut" 
  ) %>%
  group_by(datetime, fire_class,species) %>%
  summarize(mean_value = mean(value))


plot <- ggplot(filtered_data, aes(x = datetime, y = mean_value)) +
  geom_line(aes(group = fire_class, color = species)) +
  scale_color_manual(values = c(
    "Control" = "#7876B1"
  )) +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
  facet_wrap(vars(fire_class), ncol = 3, scales = "free") +
  labs(x = "Date", y = " Soil Temperature (Celsius)")+
  ylim(-10, 30)

ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")

##soil temp
file_name <- paste("loggers_soil_temperature_control_comparaison", age_vector[i], ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "soil_temperature" &
      datetime > "2023-04-23" &
      species == "Control" &
      cutting != "cut" 
  ) %>%
  group_by(datetime, fire_class, species) %>%
  summarize(mean_value = mean(value))


plot <- ggplot(filtered_data, aes(x = datetime, y = mean_value)) +
  geom_line(aes(group = fire_class, color = species)) +
  scale_color_manual(values = c(
    "Control" = "#7876B1"
  )) +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
  facet_wrap(vars(fire_class), ncol = 3, scales = "free") +
  labs(x = "Date", y = " Soil Temperature (Celsius)")+
  ylim(-10, 30)

ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")

##soil moisture
file_name <- paste("loggers_soil_moisture_control_comparaison", age_vector[i], ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "soil_moisture" &
      datetime > "2023-04-23" &
      species == "Control" &
      cutting != "cut" 
  ) %>%
  group_by(datetime, fire_class, species) %>%
  summarize(mean_value = mean(value))


plot <- ggplot(filtered_data, aes(x = datetime, y = mean_value)) +
  geom_line(aes(group = fire_class, color = species)) +
  scale_color_manual(values = c(
    "Control" = "#7876B1"
  )) +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
  facet_wrap(vars(fire_class), ncol = 3, scales = "free") +
    labs(x = "Date", y = " Soil Moisture (Celsius)")+
  ylim(0.15, 0.6)

ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")
```

```{r control_fire_class_comp_same_plot}

#air_temp
file_name <- paste("loggers_air_temperature_control_comparaison_same", age_vector[i], ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "air_temperature" &
      datetime > "2023-04-23" &
      species == "Control" &
      cutting != "cut" 
  ) %>%
  group_by(datetime, fire_class, species) %>%
  summarize(mean_value = mean(value))


plot <- ggplot(filtered_data, aes(x = datetime, y = mean_value)) +
  geom_line(aes(group = fire_class, color = fire_class)) +
  scale_color_manual(values = c(
    "Pioneer" = "#1276B1",
    "Building" = "#C11010",
    "Mature" = "#12B612"
  )) +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
    labs(title ="Mean Temperature for Control loggers depending on fire_class",x = "Date", y = " Air Temperature (Celsius)", colour = "fire_class")+
  ylim(-10, 30)

ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")

#ground_temp
file_name <- paste("loggers_ground_temperature_control_comparaison_same", age_vector[i], ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "ground_temperature" &
      datetime > "2023-04-23" &
      species == "Control" &
      cutting != "cut" 
  ) %>%
  group_by(datetime, fire_class, species) %>%
  summarize(mean_value = mean(value))


plot <- ggplot(filtered_data, aes(x = datetime, y = mean_value)) +
  geom_line(aes(group = fire_class, color = fire_class)) +
  scale_color_manual(values = c(
    "Pioneer" = "#1276B1",
    "Building" = "#C11010",
    "Mature" = "#12B612"
  )) +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
    labs(title ="Mean Temperature for Control loggers depending on fire_class",x = "Date", y = "Ground Temperature (Celsius)", colour = "fire_class")+
  ylim(-10, 30)

ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")


#soil_temp
file_name <- paste("loggers_soil_temperature_control_comparaison_same", age_vector[i], ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "air_temperature" &
      datetime > "2023-04-23" &
      species == "Control" &
      cutting != "cut" 
  ) %>%
  group_by(datetime, fire_class, species) %>%
  summarize(mean_value = mean(value))


plot <- ggplot(filtered_data, aes(x = datetime, y = mean_value)) +
  geom_line(aes(group = fire_class, color = fire_class)) +
  scale_color_manual(values = c(
    "Pioneer" = "#1276B1",
    "Building" = "#C11010",
    "Mature" = "#12B612"
  )) +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
  labs(title ="Mean Temperature for Control loggers depending on fire_class",x = "Date", y = " Soil Temperature (Celsius)", colour = "fire_class")+
  ylim(-10, 30)

ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")


#air_temp
file_name <- paste("loggers_soil_moisture_control_comparaison_same", age_vector[i], ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "soil_moisture" &
      datetime > "2023-04-23" &
      species == "Control" &
      cutting != "cut" 
  ) %>%
  group_by(datetime, fire_class, species) %>%
  summarize(mean_value = mean(value))


plot <- ggplot(filtered_data, aes(x = datetime, y = mean_value)) +
  geom_line(aes(group = fire_class, color = fire_class)) +
  scale_color_manual(values = c(
    "Pioneer" = "#1276B1",
    "Building" = "#C11010",
    "Mature" = "#12B612"
  )) +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
  labs(title ="Mean Soil Moisture for Control loggers depending on fire_class",x = "Date", y = " Soil Moisture")+
  ylim(0.15, 0.6)

ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")


```

Here it averages the combined 4 species (excludes "Control" loggers) and plots them according to fire_class / drt_treatment.

```{r mean_species_fire_class_drt_treatment}

#air_temp
file_name <- paste("loggers_air_temperature_mean_species", age_vector[i], ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "air_temperature" &
      datetime > "2023-04-23" &
      cutting != "cut" &
      !is.na(drt_treatment) &
      species != "Control"
  ) %>%
  group_by(fire_class, drt_treatment, datetime) %>%
  summarize(mean_value = mean(value))

plot <- ggplot(filtered_data, aes(x = datetime, y = mean_value)) +
  geom_line(aes(group = fire_class, color = fire_class)) +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
    labs(title ="Mean Air Temperature of every species",x = "Date", y = " Air Temperature (Celsius)")+
  facet_grid(drt_treatment ~ fire_class, scale="free")+
  ylim(-10, 30)

ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")

#ground_temp
file_name <- paste("loggers_ground_temperature_mean_species", age_vector[i], ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "ground_temperature" &
      datetime > "2023-04-23" &
      cutting != "cut" &
      !is.na(drt_treatment)&
      species != "Control"
  ) %>%
  group_by(fire_class, drt_treatment, datetime) %>%
  summarize(mean_value = mean(value))

plot <- ggplot(filtered_data, aes(x = datetime, y = mean_value)) +
  geom_line(aes(group = fire_class, color = fire_class)) +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
    labs(title ="Mean Ground Temperature of every species",x = "Date", y = "Ground Temperature (Celsius)")+
  facet_grid(drt_treatment ~ fire_class, scale="free")+
  ylim(-10, 30)

ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")

#soil_temp
file_name <- paste("loggers_soil_temperature_mean_species", age_vector[i], ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "soil_temperature" &
      datetime > "2023-04-23" &
      cutting != "cut" &
      !is.na(drt_treatment)&
      species != "Control"
  ) %>%
  group_by(fire_class, drt_treatment, datetime) %>%
  summarize(mean_value = mean(value))

plot <- ggplot(filtered_data, aes(x = datetime, y = mean_value)) +
  geom_line(aes(group = fire_class, color = fire_class)) +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
    labs(title ="Mean Soil Temperature of every species",x = "Date", y = " Soil Temperature (Celsius)")+
  facet_grid(drt_treatment ~ fire_class, scale="free")+
  ylim(-10, 30)

ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")

#soil_moisture
file_name <- paste("loggers_soil_moisture_mean_species", age_vector[i], ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "soil_moisture" &
      datetime > "2023-04-23" &
      cutting != "cut" &
      !is.na(drt_treatment)&
      species != "Control"
  ) %>%
  group_by(fire_class, drt_treatment, datetime) %>%
  summarize(mean_value = mean(value))

plot <- ggplot(filtered_data, aes(x = datetime, y = mean_value)) +
  geom_line(aes(group = fire_class, color = fire_class)) +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
    labs(title ="Mean soil moisture of every species",x = "Date", y = " Soil Moisture")+
  facet_grid(drt_treatment ~ fire_class, scale="free")+
  ylim(0.15, 0.6)

ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")

```
Her the average for every separated species is taking for each drt_treatment in each fire_class.

```{r mean_per_species_fire_class_drt_treatment}

#air_temp
file_name <- paste("loggers_air_temperature_mean_per_species",".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "air_temperature" &
      datetime > "2023-04-23" &
      cutting != "cut" &
      !is.na(drt_treatment)
  ) %>%
  group_by(fire_class, drt_treatment, species, datetime) %>%
  summarize(mean_value = mean(value))

plot <- ggplot(filtered_data, aes(x = datetime, y = mean_value)) +
  geom_line(aes(group = species, color = species)) +
  scale_color_manual(values = c(
      "Control" = "#7876B1",
      "Calluna vulgaris" = "#E18727",
      "Empetrum nigrum" = "#20854E",
      "Vaccinium vitis idea" = "#BC3C29",
      "Vaccinium myrtillus" = "#0072B5"
    )) +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
    labs(title ="Mean Air Temperature of every species",x = "Date", y = " Air Temperature (Celsius)")+
  facet_grid(drt_treatment ~ fire_class, scale="free")+
  ylim(-10, 30)

ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")

#ground_temp
file_name <- paste("loggers_ground_temperature_mean_per_species",".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "ground_temperature" &
      datetime > "2023-04-23" &
      cutting != "cut" &
      !is.na(drt_treatment)
  ) %>%
  group_by(fire_class, drt_treatment, species, datetime) %>%
  summarize(mean_value = mean(value))

plot <- ggplot(filtered_data, aes(x = datetime, y = mean_value)) +
  geom_line(aes(group = species, color = species)) +
  scale_color_manual(values = c(
      "Control" = "#7876B1",
      "Calluna vulgaris" = "#E18727",
      "Empetrum nigrum" = "#20854E",
      "Vaccinium vitis idea" = "#BC3C29",
      "Vaccinium myrtillus" = "#0072B5"
    )) +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
    labs(title ="Mean Ground Temperature of every species",x = "Date", y = " Ground Temperature (Celsius)")+
  facet_grid(drt_treatment ~ fire_class, scale="free")+
  ylim(-10, 30)

ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")

#soil_temp
file_name <- paste("loggers_soil_temperature_mean_per_species",".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "soil_temperature" &
      datetime > "2023-04-23" &
      cutting != "cut" &
      !is.na(drt_treatment) & 
      !is.na(value)
  ) %>%
  group_by(fire_class, drt_treatment, species, datetime) %>%
  summarize(mean_value = mean(value))

plot <- ggplot(filtered_data, aes(x = datetime, y = mean_value)) +
  geom_line(aes(group = species, color = species)) +
  scale_color_manual(values = c(
      "Control" = "#7876B1",
      "Calluna vulgaris" = "#E18727",
      "Empetrum nigrum" = "#20854E",
      "Vaccinium vitis idea" = "#BC3C29",
      "Vaccinium myrtillus" = "#0072B5"
    )) +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
    labs(title ="Mean Soil Temperature of every species",x = "Date", y = " Soil Temperature (Celsius)")+
  facet_grid(drt_treatment ~ fire_class, scale="free")+
  ylim(-10, 30)

ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")

#soil_moisture
file_name <- paste("loggers_soil_moisture_mean_per_species",".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "soil_moisture" &
      datetime > "2023-04-23" &
      cutting != "cut" &
      !is.na(drt_treatment)& 
      !is.na(value)
  ) %>%
  group_by(fire_class, drt_treatment, species, datetime) %>%
  summarize(mean_value = mean(value))

plot <- ggplot(filtered_data, aes(x = datetime, y = mean_value)) +
  geom_line(aes(group = species, color = species)) +
  scale_color_manual(values = c(
      "Control" = "#7876B1",
      "Calluna vulgaris" = "#E18727",
      "Empetrum nigrum" = "#20854E",
      "Vaccinium vitis idea" = "#BC3C29",
      "Vaccinium myrtillus" = "#0072B5"
    )) +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
    labs(title ="Mean soil moisture of every species",x = "Date", y = " Soil moisture")+
  facet_grid(drt_treatment ~ fire_class, scales="free")

ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")
```
temporary code just in case you wanna do something at one point
```{r temporary}


#air_temp

file_name <- paste("loggers_air_temperature_mean_species_test2", ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "air_temperature" &
      datetime > "2023-04-23" &
      cutting != "cut" &
      !is.na(drt_treatment) &
      species != "Control"
  ) %>%
  group_by(fire_class, drt_treatment, datetime) %>%
  summarize(mean_value = mean(value))

filtered_data$drt_treatment <- factor(filtered_data$drt_treatment)

plot <- ggplot(filtered_data, aes(x = datetime, y = mean_value)) +
  geom_line(aes(group = drt_treatment, color = drt_treatment)) +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
   scale_color_manual(values = c(
        "0" = "#7876B1",
        "50" = "#E18727",
        "90" = "#20854E"
      )) +
    labs(title ="Mean Air Temperature of every species",x = "Date", y = " Air Temperature (Celsius)")+
  facet_wrap(~fire_class)+
  ylim(-10, 30)

ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")

#ground_temp
file_name <- paste("loggers_ground_temperature_mean_species_test2", ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "ground_temperature" &
      datetime > "2023-04-23" &
      cutting != "cut" &
      !is.na(drt_treatment)&
      species != "Control"
  ) %>%
  group_by(fire_class, drt_treatment, datetime) %>%
  summarize(mean_value = mean(value))

filtered_data$drt_treatment <- factor(filtered_data$drt_treatment)

plot <- ggplot(filtered_data, aes(x = datetime, y = mean_value)) +
  geom_line(aes(group = drt_treatment, color = drt_treatment)) +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
   scale_color_manual(values = c(
        "0" = "#7876B1",
        "50" = "#E18727",
        "90" = "#20854E"
      )) +
    labs(title ="Mean Air Temperature of every species",x = "Date", y = " Air Temperature (Celsius)")+
  facet_wrap(~fire_class)+
  ylim(-10, 30)

ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")

#soil_temp
file_name <- paste("loggers_soil_temperature_mean_species_test2", ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "soil_temperature" &
      datetime > "2023-04-23" &
      cutting != "cut" &
      !is.na(drt_treatment) &
      species != "Control"
  ) %>%
  group_by(fire_class, drt_treatment, datetime) %>%
  summarize(mean_value = mean(value))

filtered_data$drt_treatment <- factor(filtered_data$drt_treatment)

plot <- ggplot(filtered_data, aes(x = datetime, y = mean_value)) +
  geom_line(aes(group = drt_treatment, color = drt_treatment)) +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
   scale_color_manual(values = c(
        "0" = "#7876B1",
        "50" = "#E18727",
        "90" = "#20854E"
      )) +
    labs(title ="Mean Air Temperature of every species",x = "Date", y = " Air Temperature (Celsius)")+
  facet_wrap(~fire_class)+
  ylim(4, 15)

ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")
#soil_moisture
file_name <- paste("loggers_soil_moisture_mean_species_test2", ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "soil_moisture" &
      datetime > "2023-04-23" &
      cutting != "cut" &
      !is.na(drt_treatment)&
      species != "Control"
  ) %>%
  group_by(fire_class, drt_treatment, datetime) %>%
  summarize(mean_value = mean(value))

filtered_data$drt_treatment <- factor(filtered_data$drt_treatment)

plot <- ggplot(filtered_data, aes(x = datetime, y = mean_value)) +
  geom_line(aes(group = drt_treatment, color = drt_treatment)) +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
   scale_color_manual(values = c(
        "0" = "#7876B1",
        "50" = "#E18727",
        "90" = "#20854E"
      )) +
    labs(title ="Mean soil moisture of every species",x = "Date", y = " Air Temperature (Celsius)")+
  facet_wrap(~fire_class)+
  ylim(0.15,0.6)

ggsave(file.path("data/plots", file_name), plot, height = 40, width = 80, units = "cm")

```
```{r senja_per_species_forest}


#air_temp

file_name <- paste("loggers_air_temperature_senja_perspecies_forest", ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "air_temperature" &
    datetime > "2023-07-11" &
    cutting != "cut" &
    site == "Senja" & 
    land_type == "Forested"
  ) %>%
  group_by(species)

plot <- ggplot(filtered_data, aes(x = datetime, y = value, color = as.factor(plotID))) +
  geom_line() +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
  scale_color_manual(values = c(
    "1" = "#7876B1",
    "2" = "#E18727",
    "3" = "#20854E",
    "4" = "#E1E100",
    "5" = "#E51010"
  )) +
  facet_wrap(~species) +
  ylim(0, 40)

ggsave(file.path("data/plots/senja", file_name), plot, height = 40, width = 80, units = "cm")

#ground_temp
file_name <- paste("loggers_ground_temperature_senja_perspecies_forest", ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "ground_temperature" &
    datetime > "2023-07-11" &
    cutting != "cut" &
    site == "Senja" & 
    land_type == "Forested"
  ) %>%
  group_by(species)

plot <- ggplot(filtered_data, aes(x = datetime, y = value, color = as.factor(plotID))) +
  geom_line() +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
  scale_color_manual(values = c(
    "1" = "#7876B1",
    "2" = "#E18727",
    "3" = "#20854E",
    "4" = "#E1E100",
    "5" = "#E51010"
  )) +
  facet_wrap(~species) +
  ylim(0, 40)

ggsave(file.path("data/plots/senja", file_name), plot, height = 40, width = 80, units = "cm")


#soil_temp
file_name <- paste("loggers_soil_temperature_senja_perspecies_forest", ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "soil_temperature" &
    datetime > "2023-07-11" &
    cutting != "cut" &
    site == "Senja" & 
    land_type == "Forested"
  ) %>%
  group_by(species)

plot <- ggplot(filtered_data, aes(x = datetime, y = value, color = as.factor(plotID))) +
  geom_line() +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
  scale_color_manual(values = c(
    "1" = "#7876B1",
    "2" = "#E18727",
    "3" = "#20854E",
    "4" = "#E1E100",
    "5" = "#E51010"
  )) +
  facet_wrap(~species) +
  ylim(0, 40)

ggsave(file.path("data/plots/senja", file_name), plot, height = 40, width = 80, units = "cm")

#soil_moisture
file_name <- paste("loggers_soil_moisture_senja_perspecies_forest", ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "soil_moisture" &
    datetime > "2023-07-11" &
    cutting != "cut" &
    site == "Senja" & 
    land_type == "Forested"
  ) %>%
  group_by(species)

plot <- ggplot(filtered_data, aes(x = datetime, y = value, color = as.factor(plotID))) +
  geom_line() +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
  scale_color_manual(values = c(
    "1" = "#7876B1",
    "2" = "#E18727",
    "3" = "#20854E",
    "4" = "#E1E100",
    "5" = "#E51010"
  )) +
  facet_wrap(~species) +
  ylim(0.05, 0.6)

ggsave(file.path("data/plots/senja", file_name), plot, height = 40, width = 80, units = "cm")
```

```{r per_species_open}
#air_temp

file_name <- paste("loggers_air_temperature_senja_perspecies_open", ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "air_temperature" &
    datetime > "2023-07-11" &
    cutting != "cut" &
    site == "Senja" & 
    land_type == "Open"
  ) %>%
  group_by(species)

plot <- ggplot(filtered_data, aes(x = datetime, y = value, color = as.factor(plotID))) +
  geom_line() +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
  scale_color_manual(values = c(
    "1" = "#7876B1",
    "2" = "#E18727",
    "3" = "#20854E",
    "4" = "#E1E100",
    "5" = "#E51010"
  )) +
  facet_wrap(~species) +
  ylim(0, 40)

ggsave(file.path("data/plots/senja", file_name), plot, height = 40, width = 80, units = "cm")

#ground_temp
file_name <- paste("loggers_ground_temperature_senja_perspecies_open", ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "ground_temperature" &
    datetime > "2023-07-11" &
    cutting != "cut" &
    site == "Senja" & 
    land_type == "Open"
  ) %>%
  group_by(species)

plot <- ggplot(filtered_data, aes(x = datetime, y = value, color = as.factor(plotID))) +
  geom_line() +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
  scale_color_manual(values = c(
    "1" = "#7876B1",
    "2" = "#E18727",
    "3" = "#20854E",
    "4" = "#E1E100",
    "5" = "#E51010"
  )) +
  facet_wrap(~species) +
  ylim(0, 40)

ggsave(file.path("data/plots/senja", file_name), plot, height = 40, width = 80, units = "cm")


#soil_temp
file_name <- paste("loggers_soil_temperature_senja_perspecies_open", ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "soil_temperature" &
    datetime > "2023-07-11" &
    cutting != "cut" &
    site == "Senja" & 
    land_type == "Open"
  ) %>%
  group_by(species)

plot <- ggplot(filtered_data, aes(x = datetime, y = value, color = as.factor(plotID))) +
  geom_line() +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
  scale_color_manual(values = c(
    "1" = "#7876B1",
    "2" = "#E18727",
    "3" = "#20854E",
    "4" = "#E1E100",
    "5" = "#E51010"
  )) +
  facet_wrap(~species) +
  ylim(0, 40)

ggsave(file.path("data/plots/senja", file_name), plot, height = 40, width = 80, units = "cm")

#soil_moisture
file_name <- paste("loggers_soil_moisture_senja_perspecies_open", ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "soil_moisture" &
    datetime > "2023-07-11" &
    cutting != "cut" &
    site == "Senja" & 
    land_type == "Open"
  ) %>%
  group_by(species)

plot <- ggplot(filtered_data, aes(x = datetime, y = value, color = as.factor(plotID))) +
  geom_line() +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
  scale_color_manual(values = c(
    "1" = "#7876B1",
    "2" = "#E18727",
    "3" = "#20854E",
    "4" = "#E1E100",
    "5" = "#E51010"
  )) +
  facet_wrap(~species) +
  ylim(0.05, 0.6)

ggsave(file.path("data/plots/senja", file_name), plot, height = 40, width = 80, units = "cm")
```

```{r mean_forest_vs_open_per_species}
#air_temp

file_name <- paste("loggers_air_temperature_senja_perspecies_open_vs_forest", ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "air_temperature" &
    datetime > "2023-07-11" &
    cutting != "cut" &
    site == "Senja" 

  ) %>%
  group_by(species) %>%
  

plot <- ggplot(filtered_data, aes(x = datetime, y = value, color = as.factor(plotID))) +
  geom_line() +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
  scale_color_manual(values = c(
    "1" = "#7876B1",
    "2" = "#E18727",
    "3" = "#20854E",
    "4" = "#E1E100",
    "5" = "#E51010"
  )) +
  facet_wrap(~species) +
  ylim(0, 40)

ggsave(file.path("data/plots/senja", file_name), plot, height = 40, width = 80, units = "cm")

#ground_temp
file_name <- paste("loggers_ground_temperature_senja_perspecies_open", ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "ground_temperature" &
    datetime > "2023-07-11" &
    cutting != "cut" &
    site == "Senja" & 
    land_type == "Open"
  ) %>%
  group_by(species)

plot <- ggplot(filtered_data, aes(x = datetime, y = value, color = as.factor(plotID))) +
  geom_line() +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
  scale_color_manual(values = c(
    "1" = "#7876B1",
    "2" = "#E18727",
    "3" = "#20854E",
    "4" = "#E1E100",
    "5" = "#E51010"
  )) +
  facet_wrap(~species) +
  ylim(0, 40)

ggsave(file.path("data/plots/senja", file_name), plot, height = 40, width = 80, units = "cm")


#soil_temp
file_name <- paste("loggers_soil_temperature_senja_perspecies_open", ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "soil_temperature" &
    datetime > "2023-07-11" &
    cutting != "cut" &
    site == "Senja" & 
    land_type == "Open"
  ) %>%
  group_by(species)

plot <- ggplot(filtered_data, aes(x = datetime, y = value, color = as.factor(plotID))) +
  geom_line() +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
  scale_color_manual(values = c(
    "1" = "#7876B1",
    "2" = "#E18727",
    "3" = "#20854E",
    "4" = "#E1E100",
    "5" = "#E51010"
  )) +
  facet_wrap(~species) +
  ylim(0, 40)

ggsave(file.path("data/plots/senja", file_name), plot, height = 40, width = 80, units = "cm")

#soil_moisture
file_name <- paste("loggers_soil_moisture_senja_perspecies_open", ".png", sep = "")

filtered_data <- microclimate %>%
  filter(
    sensor == "soil_moisture" &
    datetime > "2023-07-11" &
    cutting != "cut" &
    site == "Senja" & 
    land_type == "Open"
  ) %>%
  group_by(species)

plot <- ggplot(filtered_data, aes(x = datetime, y = value, color = as.factor(plotID))) +
  geom_line() +
  scale_x_datetime(date_breaks = "1 week", minor_breaks = "1 day", date_labels = "%e/%m/%y") +
  scale_color_manual(values = c(
    "1" = "#7876B1",
    "2" = "#E18727",
    "3" = "#20854E",
    "4" = "#E1E100",
    "5" = "#E51010"
  )) +
  facet_wrap(~species) +
  ylim(0.05, 0.6)

ggsave(file.path("data/plots/senja", file_name), plot, height = 40, width = 80, units = "cm")
```

```{r box_plot_tryout}

micro_data <- microclimate %>%
  filter(cutting != "cut" & datetime > "2023-06-27" & datetime < "2023-07-19" & date_in < "2023-07-01" & land_type != "DroughtNet") %>%
  mutate(daytime = floor_date(datetime, "day") ) %>%
  group_by(loggerID, daytime, site, land_type,species) %>%
  summarise(
    air_temperature_mean = mean(value[sensor == "air_temperature"]),
    air_temperature_min = min(value[sensor == "air_temperature"]),
    air_temperature_max = max(value[sensor == "air_temperature"]),
    air_temperature_range = max(value[sensor == "air_temperature"]) - min(value[sensor == "air_temperature"]),
    ground_temperature_mean = mean(value[sensor == "ground_temperature"]),
    ground_temperature_min = min(value[sensor == "ground_temperature"]),
    ground_temperature_max = max(value[sensor == "ground_temperature"]),
    ground_temperature_range = max(value[sensor == "ground_temperature"]) - min(value[sensor == "ground_temperature"]),
    soil_temperature_mean = mean(value[sensor == "soil_temperature"]),
    soil_temperature_min = min(value[sensor == "soil_temperature"]),
    soil_temperature_max = max(value[sensor == "soil_temperature"]),
    soil_temperature_range = max(value[sensor == "soil_temperature"]) - min(value[sensor == "soil_temperature"]),
    soil_moisture_mean = mean(value[sensor == "soil_moisture"]),
    soil_moisture_min = min(value[sensor == "soil_moisture"]),
    soil_moisture_max = max(value[sensor == "soil_moisture"]),
    soil_moisture_range = max(value[sensor == "soil_moisture"]) - min(value[sensor == "soil_moisture"]),
  )

micro_data <- micro_data %>%
     mutate(below_zero_air = ifelse(air_temperature_min < 0.5, 1, 0)) %>%
     mutate(below_zero_ground = ifelse(ground_temperature_min < 0.5, 1, 0)) %>%
     mutate(below_zero_soil = ifelse(soil_temperature_min < 0.5, 1, 0))

```
```{r plot_site_by_landtype}


base_air <- ggplot(micro_data, aes(x = land_type, y = air_temperature_mean, fill = land_type))
graph_air <- base_air + 
  geom_boxplot(outlier.shape = NA) +
  labs(y = "Air Temperature +15cm (C)",x="Type of the land") +
  theme_bw() +
  scale_x_discrete(labels = c("Forested" = "Forested", "Open" = "Open")) +
  facet_wrap(~site, ncol = 3, scales = "free_x") +
  scale_fill_manual(values = c("Forested" = "#1e90ff", "Open" = "#ff0800"))

ggsave(file.path("data/plots", "By_site_by_landtype_air_temp.png"), graph_air, height = 40, width = 80, units = "cm")

base_ground <- ggplot(micro_data, aes(x = land_type, y = ground_temperature_mean, fill = land_type))
graph_ground <- base_ground+ 
  geom_boxplot(outlier.shape = NA) +
  labs(y = "Ground Temperature +2cm (C)",x="Type of the land") +
  theme_bw() +
  scale_x_discrete(labels = c("Forested" = "Forested", "Open" = "Open")) +
  facet_wrap(~site, ncol = 3, scales = "free_x") +
  scale_fill_manual(values = c("Forested" = "#1e90ff", "Open" = "#ff0800"))

ggsave(file.path("data/plots", "By_site_by_landtype_ground_temp.png"), graph_ground, height = 40, width = 80, units = "cm")

base_soil <- ggplot(micro_data, aes(x = land_type, y = soil_temperature_mean, fill = land_type))
graph_soil <- base_soil + 
  geom_boxplot(outlier.shape = NA) +
  labs(y = "Soil Temperature -6cm (C)",x="Type of the land") +
  theme_bw() +
  scale_x_discrete(labels = c("Forested" = "Forested", "Open" = "Open")) +
  facet_wrap(~site, ncol = 3, scales = "free_x") +
  scale_fill_manual(values = c("Forested" = "#1e90ff", "Open" = "#ff0800"))

ggsave(file.path("data/plots", "By_site_by_landtype_soil_temp.png"), graph_soil, height = 40, width = 80, units = "cm")

base_moist <- ggplot(micro_data, aes(x = land_type, y = soil_moisture_mean, fill = land_type))
graph_moist <- base_moist + 
  geom_boxplot(outlier.shape = NA) +
  labs(y = "Soil Moisture (C)",x="Type of the land") +
  theme_bw() +
  scale_x_discrete(labels = c("Forested" = "Forested", "Open" = "Open")) +
  facet_wrap(~site, ncol = 3, scales = "free_x") +
  scale_fill_manual(values = c("Forested" = "#1e90ff", "Open" = "#ff0800"))

ggsave(file.path("data/plots", "By_site_by_landtype_soil_moist.png"), graph_moist, height = 40, width = 80, units = "cm")


```

```{r sup}
#LOGGERS WITH NO METADATA

to_sup <- microclimate %>%
  filter(is.na(land_type)) %>%
  group_by(loggerID) %>%
  distinct(loggerID)

to_sup <- micro_data %>%
  filter(is.infinite(soil_moisture_min)) %>%
  distinct(loggerID)

```

```{r species_test}
base_air_species <- ggplot(micro_data, aes(x = land_type, y = air_temperature_mean,fill=species))
graph_air_species <- base_air_species + 
  geom_boxplot() +
  scale_fill_manual(values = c("#1e90ff","#ff0800","#E2E010","#10E110"))+ 
    facet_wrap(~site, scales = "free_x") +
  labs(y = "Air Temperature +15cm (C)",x="Type of the land") +
  theme_bw() 

  

ggsave(file.path("data/plots", "By_site_species_air_temp.png"), graph_air_species, height = 40, width = 80, units = "cm")

base_ground_species <- ggplot(micro_data, aes(x = land_type, y = ground_temperature_mean,fill=species))
graph_ground_species <- base_ground_species + 
  geom_boxplot() +
  scale_fill_manual(values = c("#1e90ff","#ff0800","#E2E010","#10E110"))+ 
    facet_wrap(~site, scales = "free_x") +
  labs(y = "Ground Temperature +2cm (C)",x="Type of the land") +
  theme_bw() 

  

ggsave(file.path("data/plots", "By_site_species_ground_temp.png"), graph_ground_species, height = 40, width = 80, units = "cm")
# 

base_soil_species <- ggplot(micro_data, aes(x = land_type, y = soil_temperature_mean,fill=species))
graph_soil_species <- base_soil_species + 
  geom_boxplot() +
  scale_fill_manual(values = c("#1e90ff","#ff0800","#E2E010","#10E110"))+ 
    facet_wrap(~site, scales = "free_x") +
  labs(y = "Soil Temperature -6 (C)",x="Type of the land") +
  theme_bw() 

  

ggsave(file.path("data/plots", "By_site_species_soil_temp.png"), graph_air_species, height = 40, width = 80, units = "cm")
# 
base_soil_moisture_species <- ggplot(micro_data, aes(x = land_type, y = soil_moisture_mean,fill=species))
graph_soil_moisture_species <- base_soil_moisture_species + 
  geom_boxplot() +
  scale_fill_manual(values = c("#1e90ff","#ff0800","#E2E010","#10E110"))+ 
    facet_wrap(~site, scales = "free_x") +
  labs(y = "Air Temperature +15cm (C)",x="Type of the land") +
  theme_bw() 

  

ggsave(file.path("data/plots", "By_site_species_soil_moisture.png"), graph_air_species, height = 40, width = 80, units = "cm")

```

